\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-2pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% Preamble (for reference):
% \usepackage{fontawesome5}
% \usepackage[hidelinks]{hyperref}
% \hypersetup{pdfnewwindow=true}

%----------HEADING-----------------
\begin{center}
  % Name centered
  \textbf{\Large \underline{\href{https://rahulwrites.onrender.com}{RAHUL SHARMA}}}
  \\[6pt]
  % One-line, centered contact info with reduced spacing
  \small
  \makebox[\linewidth][c]{%
    \textbf{Phone:} +91 8291147114 \hspace{0.8cm}%
    \faGithub\hspace{0.2em}\underline{\href{https://github.com/rahul122703}{ github.com/rahul122703}} \hspace{0.8cm}%
    \underline{\href{mailto:rsharma122703@gmail.com}{rsharma122703@gmail.com}} \hspace{0.8cm}%
    \faLinkedin\hspace{0.2em}\underline{\href{https://www.linkedin.com/in/rahul122703/}{ linkedin.com/in/rahul122703}}%
  }
\end{center}

%--------SKILLS------------
\section*{Technical skills}
{\small
\noindent
\textbf{Frontend :}\quad React.js , TailwindCSS , Bootstrap  \\
\textbf{Testing \& Scraping :}\quad Selenium , BeautifulSoup\\ 
\textbf{Languages \& Tools :}\quad JavaScript , C++ , Python , SQL , Git\\
\textbf{Backend \& APIs :}\quad Flask , Django REST Framework , Next.js , Postman\\
}

%-----------PROJECTS-----------------
\section{Projects}
\begin{itemize}

  \item \textbf{RahulMart} \hfill
    \underline{\href{https://rahulmart.netlify.app}{LIVE\_LINK}} \hspace{0.3cm}
    \underline{\href{https://github.com/Rahul122703/rahulmart}{CODE}} \\
  \textit{React.js , TailwindCSS , Serverless Functions , Airtable}

  An e-commerce web app built using React and Airtable. It lets users browse, search, and shop for products with useful features and a clean, modern layout.

  \textbf{Features:} Stripe Payment integration, Airtable backend integration, OAuth, dynamic product listings, category filtering, price and name sorting, Search feature, dark mode toggle.

  \item \textbf{PollVerse} \hfill
    \underline{\href{https://pollversey.onrender.com}{LIVE\_LINK}} \hspace{0.3cm}
    \underline{\href{https://github.com/Rahul122703/pollverse}{CODE}} \\
  \textit{HTML, CSS, JS , Flask , SQLAlchemy , Matplotlib , Werkzeug}

  A web app for sentiment analysis in anonymous polls and discussions, providing insights into user feedback over time.

  \textbf{Features:} Anonymous Polls with OTP login, Incognito Mode, Sentiment Analysis, User Profiles with personal poll tracking and email notifications.

  \item \textbf{ShareSense} \hfill
  \underline{\href{https://sharesense.onrender.com}{LIVE\_LINK}} \hspace{0.3cm}
  \underline{\href{https://github.com/Rahul122703/rshare}{CODE}} \\
  \textit{React.js , Flask , SQLAlchemy , Werkzeug}

  A Flask-based platform to securely share documents without needing WhatsApp. Users can upload files anonymously or via OTP-secured login.

  \textbf{Features:} Public/private file sharing, OTP login, drag-and-drop uploads, 50+ files at once, personal file dashboard.

  % \item \textbf{Rohan Arts} \hfill
  % \underline{\href{https://rohanarts.vercel.app}{LIVE\_LINK}} \hspace{0.3cm}
  % \underline{\href{https://github.com/Rahul122703/rohan_arts}{CODE}} \\
  % \textit{HTML, CSS, JS (Vanilla)}

  % \textbf{Description:} Rohan Arts is a personal website made using only HTML, CSS, and plain JavaScript. It showcases the artist’s sketches and paintings with search and filter capabilities.

  % \textbf{Features:} Artwork filtering (sketch/painting), keyword search, responsive design, contact options, built without external frameworks.

  % \item \textbf{Elementary Apps} \hfill
  % \underline{\href{https://rahulsharmahosted.netlify.app}{LIVE\_LINK}} \hspace{0.3cm}
  % \underline{\href{https://github.com/Rahul122703/all_hosted_project_list}{CODE}} \\
  % \textit{HTML, CSS, JS, React, Flask and more}

  % \textbf{Description:} A central hub showcasing all personal projects, including full-stack apps, frontend sites, serverless tools, and Python scripts like fake news detection, tic-tac-toe, and more. 

\end{itemize}

%-----------EXPERIENCE-----------------
\section*{Experience}
\textbf{\underline{\href{https://res.cloudinary.com/dle5gmw0f/image/upload/v1751134880/kkhcertificate_ivbe5w.png}{Software Developer}} | KanoonKeHaath}\hfill \small \textbf{December 2024 - June 2025}\\[-0.5em] % Date to right, smaller font, slightly reduced vertical space
\begin{itemize}\setlength{\itemsep}{0pt} % Reduces vertical spacing between list items
    \item Developed and implemented backend \textbf{REST APIs} using Next.js and tested with Postman.
    \item Designed and built responsive user interfaces with \textbf{React.js} and \textbf{Tailwind CSS}.
    \item Used Axios for frontend data fetching and \textbf{Context API} for state management.
    \item Utilized \textbf{Git} for efficient version control, including branching strategies, resulting in merged \textbf{Pull Requests}.
\end{itemize}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading{Xavier Institute of Engineering, Mumbai}{2022 - Present}
  \resumeItemListStart
    \resumeItem{B.E. in Information Technology}{CGPA: 8.26 (Aggregate till Sem 5)}
  \resumeItemListEnd

  \resumeSubheading{Elphinstone College, Mumbai}{2022}
  \resumeItemListStart
    \resumeItem{H.S.C.}{Percentage: 61.17\%}
  \resumeItemListEnd

  \resumeSubheading{M.V. High School, Mumbai}{2019}
  \resumeItemListStart
    \resumeItem{S.S.C.}{Percentage: 77.20\%}
  \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------------
\section{Achievements}
\resumeSubHeadingListStart
  \resumeItem{\underline{Project Exhibition Winner} \href{https://res.cloudinary.com/dle5gmw0f/image/upload/v1751137649/PollverseFirstPrice_ji8usj.png}{(Certificate)}}{Won First Prize for \textbf{PollVerse} at college-level project exhibition.}
  \resumeItem{\underline{Hackathon Finalist} \href{https://res.cloudinary.com/dle5gmw0f/image/upload/v1751134881/24hrhack_ifojuw.png}{(Certificate)}}{Reached Top 4 in inter-college hackathon.}
\resumeSubHeadingListEnd

%-----------EXTRA CURRICULAR-----------------
\section{Extra-Curricular}
\resumeSubHeadingListStart
  \resumeSubheading{TPO Co-ordinator}{Aug 2024 -- Present}
    \resumeItemListStart
      \resumeItem{Role}{Organized and managed various college placement activities and student-company communications.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------HOBBIES-----------------
\section{Hobbies}
\resumeSubHeadingListStart
  \resumeItem{Chess}{\href{https://www.chess.com/member/rahul122703}{\faChess \hspace{0.1cm} \underline{chess.com/rahul122703}}}
  \resumeItem{Touch Typing}{\href{https://monkeytype.com/profile/rahul122703}{\faKeyboardO \hspace{0.1cm} \underline{monkeytype.com/rahul122703}} (100+ WPM)}
\resumeSubHeadingListEnd

\end{document}
